\section{Verification, Acceptance, and Certification} \label{sec:verify-accept-certify}

This section defines the quality metrics for calibration products and ISR outputs.
Here we define the criteria used to promote products to ``accepted'' and ``certified''.

\subsection{Data products, Distribution, and User Access} \label{sec:verify-accept-certify:data-products}
Describe the output schema, distribution process (exporting/importing, rucio, TAXICAB tracking), and user access.

We enumerate the primary data products (calibration frames, ISR outputs, masks, and metadata tables), describe naming/versioning conventions, and summarize the provenance tracked for each product (inputs, software versions, and configuration).

Briefly describe how users discover and retrieve products (e.g., via a data butler/repository interface) and recommended query patterns.

Be sure to mention that header metadata contains information about whether a particular ISR step was applied/not applied and what calibraiton dataset what used.

\subsection{Verification} \label{sec:verify-accept-certify:verification}

We list (possibly in a table) the automated verification tests for each data product (sanity checks, analysis plots, detailed plots, distributional checks, and science test images) and the thresholds that determine acceptance/rejection of different calibration data products.

\subsection{Acceptance} \label{sec:verify-accept-certify:acceptance}
This section will describe the calibration acceptance process (TAXICAB).

Describe how verified products are compared against earlier baselines to reveal regressions or deviations, and how acceptance decisions are documented.

\subsection{Certification} \label{sec:verify-accept-certify:certification}
Describe the final certification step in the context of the data ``butler'' and file system storage.

\subsection{Data Monitoring} \label{sec:verify-accept-certify:data-monitoring}
Discuss how we monitor incoming streams of new data for quality (e.g.\ rubinTV, plot navigator, trend monitoring with chronograph).

\subsection{Limitations} \label{sec:verify-accept-certify:limitations}
Summarize known limitations for DP2 (instrumental systematics not fully corrected, edge cases, missing calibrations, validity constraints) and near-term roadmap items.
